---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Classifying Penguin Data

![Build Docker](https://github.com/jonnylaw/penguins/workflows/Build%20Docker/badge.svg)

This project previously used the Iris dataset, however it's now changed to the penguins dataset. See [here](https://towardsdatascience.com/penguins-dataset-overview-iris-alternative-9453bb8c8d95) for details.

This is an example project which classifys the species of Penguin from the [Palmer penguins](https://github.com/allisonhorst/palmerpenguins) dataset. The model is fit using the [tidymodels](https://github.com/tidymodels/tidymodels) metapackage. The file `R/model.R` contains the modelling code required. The rough steps are 

* Split the data into training and test sets
* Define pre-processing steps using [recipes](https://tidymodels.github.io/recipes/)
* Create a random forest model using [parsnip](https://tidymodels.github.io/parsnip/)
* Combine the model and recipe into a [workflow](https://tidymodels.github.io/workflows/)
* Perform hyper-parameter tuning using cross validation on the training using [tune](https://tidymodels.github.io/tune/)
* Select the best model
* Fit the best model to the training data
* Save the best model

## Deployment

The application is deployed using Docker, see the Dockerfile for details. The base image is from [rocker](https://hub.docker.com/u/rocker). Dependencies are managed using [renv](https://rstudio.github.io/renv/).

```{bash, eval=FALSE}
docker build . --file Dockerfile
```

## Querying the API

The model is served using [plumber](https://www.rplumber.io/). To predict the type of flower given petal and sepal features, submit a JSON file using POST. An example using curl is below.

```{bash, eval=FALSE}
curl localhost:8000/getprediction --header "Content-Type: application/json" \
  --request POST \
  --data @data/example.json
```

## Model Performance

The data is split into a training and test set, the model is then fit on the training set. The performance measures are calculated using the test set.

```{r, echo=FALSE}
knitr::kable(readr::read_rds(path = here::here("models/test_performance.Rds")), digits = 2)
```
